An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex

\vskip 0.3in
]
% Notes:
%  redo the preprocessing experiment and explain why some techniques increase the accuracy more than others. 
\begin{abstract} 
The aim of this paper is to present a complete system for off-line handwriting recognition. 
We discuss how to segment texts with contouring. Next we present our method of segmentating words into characters. 
Then we describe how to recognise characters with a deep neural network approach. 
Finally we present some postprocessing techniques to correct mispredicted text. 
\end{abstract}

@@

@@

\section{Conclusion}

\section{Future research}
State-of-the-art systems currently use segmentation-free approaches, this involves handwriting recognition without explicitly splitting words into characters. These methods are mostly based on hidden Markov models and neural networks. This concept is explained and applied by \cite{presham}.
\section{Acknowledgements}
We thank Sarah Vluymans for her comments on this paper.
\bibliography{paper}
\bibliographystyle{icml2016}

>>>>

\vskip 0.3in
]
% Notes:
%  redo the preprocessing experiment and explain why some techniques increase the accuracy more than others. 
\begin{abstract} 
The aim of this paper is to present a complete system for off-line handwriting recognition. 
We discuss how to segment texts with contouring. Next we present our method of segmentating words into characters.
Then we describe how to recognise characters with a deep neural network approach. 
Finally we presentf postprocessing techniques to correct mispredicted text. 
\end{abstract}

@@

\begin{figure}
    \begin{subfigure}{\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{images/vpp}
    \vspace{-5px}
    \caption*{Vertical projection profile.}
    \end{subfigure}
    \begin{subfigure}{\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{images/rules}
    \vspace{-5px}
    \caption*{Rule based correction.}
    \end{subfigure}
    \begin{subfigure}{\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{images/nn}
    \vspace{-5px}
    \caption*{Correction through neural network.}
    \end{subfigure}
    \caption{Word segmentation steps}
    \label{fig:char_segm}
\end{figure}

@@

\section{Conclusion}
There are a lot of steps in this paper from which we can draw conclusions.
The segregation of a text image in word images is  
Word extraction is a problem

Character segmentation is another ..
The proposed oversegmentation serves the intended purpose, however more rule-based postprocessing steps are needed to reduce the amount of incorrect potential segmentation points the neural network has to process.

The neural network

\section{Future research}
State-of-the-art systems currently use segmentation-free approaches, this involves handwriting recognition without explicitly splitting words into characters. These methods are mostly based on hidden Markov models and neural networks.
This approach does not suffer from character segmentation artifacts
This concept is explained and applied by \cite{presham}.
\section{Acknowledgements}
We thank Sarah Vluymans for her comments on this paper.
\bibliography{paper}
\bibliographystyle{icml2016}
